upwell_IDX

### 2019-08-13 upwell_IDX.Rmd
A bit more

SACTN_upwell <- UI_angle %>% 
  dplyr::rename(t = date,
                temp = ui.saws) %>%
  group_by(site) %>%
  # mutate(min_t = min(t), 
  #        max_t = max(t)) %>% 
  nest() %>% 
  mutate(clim = purrr::map(data, ts2clm, climatologyPeriod = c("2000-01-01", "2005-12-31")),
         exceed = purrr::map(clim, exceedance, minDuration = 3, threshold = 3)) %>% 
  # mutate() %>% 
  select(-data, -clim) %>% 
  unnest()

@@

>>>>

SACTN_upwell <- UI_angle %>% 
  dplyr::rename(t = date,
                temp = ui.saws) %>%
  group_by(site) %>%
  # mutate(min_t = min(t), 
  #        max_t = max(t)) %>% 
  nest() %>% 
  mutate(clim = purrr::map(data, ts2clm, climatologyPeriod = c("2000-01-01", "2005-12-31")),
         exceed = purrr::map(clim, exceedance, minDuration = 3, threshold = 3)) %>% 
  # mutate() %>% 
  select(-data, -clim) %>% 
  unnest() %>%
  filter(row_number() %% 2 == 1) %>%
  unnest()

@@

# SACTN_upwell_metrics
